### 2017-09-05 paper/evaluation.tex
Pass on RQ5

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to process the
data and generate plots.  All source artifacts are publicly available
for replication (on our website~\cite{ourwebpage})\Comment{ at \Fix{create gh-pages}}.  This
includes supporting scripts (\eg, the script that test subjects and
generates raw analysis data) and the full list of projects. \Comment{,
  and a \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  Three
cases worth special attention: \CodeIn{Chaos}, \CodeIn{Takes} and
\CodeIn{Log4J2}.  No significant speedup was observed in
\CodeIn{Chaos}, a project with only three test classes, of which one
monopolizes the bulk of test execution time.  This project uses
configuration \ParClassSeqMeth{}, which runs test classes in parallel
and test methods, declared in each class, sequentially.  Consequently,
speedup cannot be obtained as the cost of the single expensive test
class cannot be broken down with the selected configuration. \Fix{Although
project \CodeIn{Takes} also uses configuration \ParClassParMeth{},
results obtained are very different compared to \CodeIn{Chaos}.  The
speedup observed in \CodeIn{Jcabi} was the highest amongst all
projects.  This project contains test classes with a small number of
test methods and several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.} Finally, we note that parallel
execution in \CodeIn{Log4J2} was ineffective.  We found that Maven
invokes several test modules in this project but the test modules that
dominate execution time run sequentially by default.

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
      machine setup we used, the average speedup observed with default
      configurations of parallelization was \avgSpeedup{}x.}
  \end{minipage}
}
\end{center}

>>>>

To run our experiments, we used a Core i7-4790 (3.60 GHz) Intel
processor machine with eight virtual CPUs (four cores with two native
threads each) and 16GB of memory, running Ubuntu 14.04 LTS Trusty Tahr
(64-bit version).  Software settings include \Comment{the Linux
  \emph{sysstat} package to measure performance, }git to fetch
subjects, Java 8, and Maven 3.3.9 to build and test subjects. We used
Python\Comment{ 3.4}, Bash, R and Ruby\Comment{ 2.3} to process the
data and generate plots.  All source artifacts are publicly available
for replication (on our website~\cite{ourwebpage}).  This
includes supporting scripts (\eg, the script that test subjects and
generates raw analysis data) and the full list of projects. \Comment{,
  and a \emph{Vagrantfile} to emulate our hardware and all software
  dependencies.}

@@

Results indicate that, on average, parallel execution was
\avgSpeedup{} times faster compared to sequential execution.  Three
cases worth special attention: \CodeIn{Chaos}, \CodeIn{Takes} and
\CodeIn{Log4J2}.  No significant speedup was observed in
\CodeIn{Chaos}, a project with only three test classes, of which one
monopolizes the bulk of test execution time.  This project uses
configuration \ParClassSeqMeth{}, which runs test classes in parallel
and test methods, declared in each class, sequentially.  Consequently,
speedup cannot be obtained as the cost of the single expensive test
class cannot be broken down with the selected configuration.
\Jbc{
On the other hand, the speedup observed in project \CodeIn{Takes} was
the highest amongst all projects. This subject uses configuration
\ParClassParMeth{} and contains 419 test methods distributed nearly
equally among 148 test classes with a small number of test methods.
Furthermore, several methods in those classes are time-consuming.
As result, the CPUs available for testing are kept occupied for the
most part during test execution.}
Finally, we note that parallel execution in \CodeIn{Log4J2} was
ineffective.  We found that Maven invokes several test modules in this
project but the test modules that dominate execution time run
sequentially by default.

@@

\begin{center}
\fbox{
  \begin{minipage}{8cm}
    \textit{Answering \numRQSpeedupOne{}:}~\emph{Considering the
      machine setup we used, the average speedup observed with default
      configurations of parallelization was \avgSpeedup{}x.
      \Jbc{The design of the test suite impacts the speedup obtained
      in a given parallel configuration.}
      }
  \end{minipage}
}
\end{center}
